Software variability in fMRI analysis:\\ comparing between-tool and numerical errors

### 2021-12-07 paper/paper.tex
Biblio updates, add-ons to Dice analysis, inviting Camille and Alex as co-authors

\author{Ali Salari$^1$, Yohan Chatelain$^1$, [other co-authors], Gregory Kiar$^2$, Tristan Glatard$^1$ \\
$^1$ Department of Computer-Science and Software Engineering, Concordia University, Montreal, Canada\\
$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}

>>>>

\author{Ali Salari$^1$, Yohan Chatelain$^1$, Alexander Bowring$^2$, Camille Maumet$^3$, Gregory Kiar$^4$, Tristan Glatard$^1$\\
\vspace*{0.1cm}\\
$^1$ Department of Computer-Science and Software Engineering, Concordia University, Montreal, Canada\\
$^2$ Li Ka Shing Centre for Health Information and Discovery, Nuffield Department of Population Health,\\ Big Data Institute, University of Oxford, Oxford, UK\\
$^3$ Inria, Univ Rennes, CNRS, Inserm, IRISA UMR 6074, Empenn ERL U 1228, Rennes, France\\
$^4$ Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
